\documentclass[a4paper,12pt,oneside]{book}%extreport
\usepackage{times} 
% \usepackage{multibib}
\usepackage{lipsum}
\usepackage{enumitem}
\usepackage{fancyvrb}
\usepackage{appendix}
\usepackage[shortlabels]{enumitem}
\usepackage{booktabs}
\usepackage{rotating} % Rotating table
\usepackage{hhline}
\usepackage{colortbl}
\usepackage{afterpage}
\usepackage{mathtools} %Fixes/improves amsmath
\usepackage{setspace}
\usepackage[utf8]{vietnam}
\usepackage{amstext, amsmath,latexsym,amsbsy,amssymb, amssymb,amsthm,amsfonts,multicol, nccmath}
\usepackage{listings}
\usepackage{xcolor}
\lstset{
  basicstyle=\ttfamily,
  keywordstyle=\color{blue},
  commentstyle=\color{green!60!black},
  stringstyle=\color{red},
  frame=single,
  breaklines=true,
  showstringspaces=false,
  captionpos=b
}
\usepackage[left=3cm,right=2cm,top=2.5cm,bottom=3cm,footskip=40pt]{geometry}
\usepackage{pdflscape}
\usepackage{apacite}
\usepackage{tikz}
\usepackage{array}
\newcolumntype{C}[1]{>{\centering\let\newline\\\arraybackslash\hspace{0pt}}m{#1}}
\usetikzlibrary{calc}
\usepackage{tabularx}
\usepackage{multicol}
\usepackage{array,color,colortbl}
\setcounter{secnumdepth}{4}
 %\usepackage[square,numbers]{natbib}
\usepackage[square, comma, numbers, sort&compress]{natbib}
\setlength{\parindent}{1cm}
\usepackage{color}
\usepackage{indentfirst}
\usepackage{exscale,eucal}
\usepackage{fancyhdr}
\usepackage{fncychap}
\usepackage[chapter]{algorithm}
\usepackage{multirow}
\usepackage{graphicx}
\usepackage{algpseudocode}
\usepackage{tabularx,multicol,multirow,longtable}
\usepackage{etoolbox}
\usepackage{tikz}	
\usetikzlibrary{calc,arrows,decorations.pathmorphing,backgrounds,positioning,fit,shapes,decorations.shapes, shapes.geometric, decorations.pathreplacing, decorations.text}
 
	\tikzstyle{block} = [draw,rectangle,thick,minimum height=2em,minimum width=2em,drop shadow,fill=blue!50]
	\tikzstyle{sum} = [draw,circle,inner sep=0mm,minimum size=2mm]
	\tikzstyle{connector} = [->,thick]
	\tikzstyle{line} = [very thick]
	\tikzstyle{branch} = [circle,inner sep=0pt,minimum size=1mm,fill=black,draw=black]
	\tikzstyle{axes} = [->,>=stealth',semithick]
	\tikzstyle{important line} = [very thick,draw=red]
	\tikzstyle{important text} = [rounded corners,fill=red!10,inner sep=1ex]
\usepackage{circuitikz}
\usepackage{pgfplots}
\pgfplotsset{compat=1.16}
\usepackage[numbers]{natbib}
\usepackage{titlesec}
\usepackage[labelsep=period]{caption}
\usepackage{subfigure}
\DeclareCaptionFormat{myformat}{\fontsize{13}{15}\selectfont#1#2#3}
\captionsetup{format=myformat}
\usepackage{titletoc}
\titlelabel{\thetitle.\,\,}
\titleformat{\chapter}[display] 
  {\fontsize{14}{16}\selectfont\bfseries\centering}
  {\MakeUppercase{\chaptertitlename}\ \thechapter}{0pt}{\fontsize{14}{16}\selectfont\MakeUppercase}
\titlespacing{\chapter}{0pt}{0pt}{40pt} 
\titleformat*{\section}{\fontsize{14}{14}\selectfont\bfseries}
\titleformat*{\subsection}{\fontsize{14}{14}\selectfont\bfseries}
\titleformat*{\subsubsection}{\fontsize{14}{14}\selectfont\bfseries}
\titleformat*{\paragraph}{\large\bfseries}
\titleformat*{\subparagraph}{\large\bfseries}
\graphicspath {{figures/}}

\titlespacing\section{0pt}{6pt plus 4pt minus 2pt}{1pt plus 2pt minus 2pt} 
\titlespacing\subsection{0pt}{6pt plus 4pt minus 2pt}{1pt plus 2pt minus 2pt}
\titlespacing\subsubsection{0pt}{6pt plus 4pt minus 2pt}{0pt plus 2pt minus 2pt}
\titlespacing\subsubsubsection{0pt}{6pt plus 4pt minus 2pt}{0pt plus 2pt minus 2pt}

\usepackage[subfigure]{tocloft} 

\cftsetpnumwidth{20pt}
\titlecontents{chapter}
  [0pt]
  {}
  {\fontsize{13.5}{14}\selectfont\MakeUppercase{\chaptername}\ \thecontentslabel.\,\,}
  {}
  {\cftdotfill{\cftdotsep}\contentspage} 
	\renewcommand{\cftsecaftersnum}{.}%
	\renewcommand{\cftsubsecaftersnum}{.}%

\usetikzlibrary{calc}
\newtheorem{definition}{\bf Định nghĩa}[chapter]
\newtheorem{theorem}{\bf Định lý}[chapter]
\newtheorem{lemma}{\bf Bổ đề}[chapter]

\renewcommand{\cftfigfont}{Hình~}
\renewcommand{\cfttabfont}{Bảng~ }
\floatname{algorithm}{Thuật toán}
\makeatletter
\renewcommand\@biblabel[1]{[#1]}
\renewcommand\harvardyearleft{\unskip~(}
\renewcommand\harvardyearright{\unskip )}
\makeatother
\renewcommand{\baselinestretch}{1.4}
\flushbottom
\renewcommand*{\bibfont}{\fontsize{13}{16}\selectfont}

\usepackage[hidelinks, unicode]{hyperref}
\DefineVerbatimEnvironment{SQLSyntax}{Verbatim}{
  fontsize=\fontsize{11}{13}\selectfont,
  fontfamily=tt,
  formatcom=\bfseries,
  xleftmargin=2.5em
}

% --- UNIVERSAL PREAMBLE BLOCK ---
\usepackage[a4paper, top=2.5cm, bottom=2.5cm, left=2cm, right=2cm]{geometry}
\usepackage[vietnamese, bidi=basic, provide=*]{babel}

\babelprovide[import, onchar=ids fonts]{vietnamese}
\babelprovide[import, onchar=ids fonts]{english}

% --- PACKAGES FOR CODE BOXES ---
\usepackage{xcolor}
\usepackage{listings}
\usepackage[most]{tcolorbox}

% Định nghĩa màu sắc cho code
\definecolor{codebg}{RGB}{245, 245, 245}
\definecolor{codegray}{rgb}{0.5,0.5,0.5}
\definecolor{codepurple}{rgb}{0.58,0,0.82}
\definecolor{backcolour}{rgb}{0.95,0.95,0.92}

% Cấu hình listings
\lstset{
    backgroundcolor=\color{backcolour},   
    commentstyle=\color{codegray},
    keywordstyle=\color{magenta},
    numberstyle=\tiny\color{codegray},
    stringstyle=\color{codepurple},
    basicstyle=\ttfamily\small,
    breakatwhitespace=false,         
    breaklines=true,                 
    captionpos=b,                    
    keepspaces=true,                 
    numbers=none,                    
    showspaces=false,                
    showstringspaces=false,
    showtabs=false,                  
    tabsize=2,
    frame=single,
    rulecolor=\color{black},
    framerule=0.5pt,
    framesep=5pt,
    language=SQL,
    xleftmargin=3em 
}

\begin{document}
\fontsize{13}{15.5}\selectfont

\pagestyle{empty}
\input{cover/Biangoai}
\newpage
\pagestyle{plain}
\pagenumbering{gobble}
\input{cover/Biatrong}
\newpage
\def\baselinestretch{1.2}
\pagestyle{plain}
\pagenumbering{gobble}
\input{cover/loicamdoan}
\newpage
\input{cover/loicamon} 
\newpage
\newpage
\pagenumbering{roman}


\setlength{\parindent}{1cm}
\setlength{\parskip}{0.6ex}

\fontsize{13}{16}\selectfont
\renewcommand{\contentsname}{\vspace{-70pt}\centerline{\fontsize{14}{16}\selectfont\MakeUppercase{Mục lục}}}
\clearpage
\phantomsection
\addcontentsline{toc}{chapter}{Mục lục}
\tableofcontents
\clearpage
\input{cover/tomtat}
\newpage
\clearpage
\phantomsection
\addcontentsline{toc}{chapter}{Danh mục hình vẽ}
\renewcommand{\listfigurename}{\vspace{-70pt}\centerline{\fontsize{14}{16}\selectfont{\MakeUppercase{Danh mục   hình vẽ}}}}
\listoffigures
\fontsize{13}{16}\selectfont
\newpage
\clearpage
\phantomsection
\addcontentsline{toc}{chapter}{Danh mục bảng biểu}
\renewcommand{\listtablename}{\vspace{-70pt}\centerline{\fontsize{14}{16}\selectfont{\MakeUppercase{Danh mục bảng biểu}}}}
\listoftables
\fontsize{13}{16}\selectfont
\newpage

\pagenumbering{arabic}
\pagestyle{plain}

\input{chapter/Chap0_Introduction}
\newpage
\input{chapter/Chap1_Background}
\newpage
\input{chapter/Chap2_RelatedWork}
\newpage
\input{chapter/Chap3_Design}
\newpage
\input{chapter/Chap4_Experiments}
\newpage
\input{chapter/Chap5_Conclusion}
\newpage

\appendix
% \input{cover/phuluc}
\def\baselinestretch{1}
\vspace{-2cm}
\renewcommand{\bibname}{Tài liệu tham khảo}
\clearpage
\phantomsection
\addcontentsline{toc}{chapter}{{TÀI LIỆU THAM KHẢO}}
\renewcommand{\refname}{Literary works}
\begin{thebibliography}{xx}

	\harvarditem[Rigger and Su]{Rigger and Su}{2020a}{Rigger2020a}
	Manuel Rigger and Zhendong Su. 2020a. Detecting Optimization Bugs in Database Engines via Non-Optimizing Reference
Engine Construction. In Proceedings of the 2020 28th ACM Joint Meeting on European Software Engineering Conference
and Symposium on the Foundations of Software Engineering (Sacramento, California, United States) (ESEC/FSE 2020).

	\harvarditem[Rigger and Su]{Rigger and Su}{2020b}{Rigger2020b}
	Manuel Rigger and Zhendong Su. 2020b. OOPSLA 20 Artifact for "Finding Bugs in Database Systems via Query Partitioning". https://doi.org/10.5281/zenodo.4032401

	\harvarditem[Rigger and Su]{Rigger and Su}{2020c}{Rigger2020c}
	Manuel Rigger and Zhendong Su. 2020c. Testing Database Engines via Pivoted Query Synthesis. In 14th USENIX Symposium
on Operating Systems Design and Implementation (OSDI 20). USENIX Association, Banff, Alberta. https://www.usenix.org/conference/osdi20/presentation/rigger

	\harvarditem[Jiang and Su]{Jiang and Su}{2024}{Jiang2024}
	Zu-Ming Jiang and Zhendong Su. Detecting Logic Bugs in Database Engines via Equivalent Expression Transformation. ETH Zurich.

	\harvarditem{SQLite}{2024}{SQLite}
	SQLite. https://www.sqlite.org/index.html

	\harvarditem{MySQL}{2024}{MySQL}
	MySQL. https://www.mysql.com/.

	\harvarditem{SQLancer}{2024}{SQLancer}
	SQLancer. https://github.com/sqlancer/sqlancer.

	\harvarditem{PostgreSQL}{2024}{PostgreSQL}
	PostgreSQL. https://www.postgresql.org/.

	\harvarditem{SQLite Window Functions}{2024}{SQLiteWindow}
	Sqlite Window Functions https://sqlite.org/windowfunctions.html

	\harvarditem[Gao et al.]{Gao, Liu, Cui, Li, Zhang, Wei, and Zhao}{2023}{Gao2023}
	A Comprehensive Survey on Database Management System Fuzzing:
Techniques, Taxonomy and Experimental Comparison
XIYUE GAO, ZHUANG LIU, and JIANGTAO CUI, Xidian University, China
HUI LI∗, Xidian University, China and Shanghai Yunxi Technology Co., Ltd., China
HUI ZHANG, KEWEI WEI, and KANKAN ZHAO, Inspur, China https://arxiv.org/pdf/2311.06728

\end{thebibliography}

\end{document}
